Life Expectancies for selected populations

### 2022-07-25 appendices/life_expectancy_trends.Rmd
minor edits

```{r}
hmd_ex_selected_countries_with_synth %>% 
  left_join(country_code_lookup) %>% 
  mutate(country = factor(country, levels = c("England & Wales", "Scotland", "Synthetic Germany", "Spain", "France", "Italy", "Netherlands"))) %>% 
  filter(!is.na(country)) %>% 
  filter(between(year, 1980, 2020)) %>% 
  filter(x == 0) %>% 
  ggplot(aes(x = year, y = ex, group = sex, colour = sex, linetype = sex)) + 
  geom_line() +
  facet_wrap(~country) +
  labs(
    x = "Year",
    y = "Life Expectancy at birth",
    title = "Life expectancies at birth for selected nations",
    subtitle = "1980 to 2020 or latest available year",
    caption = "Source: Human Mortality Database"
  )
```
Equivalently

@@

```{r}
hmd_ex_selected_countries_with_synth %>% 
  left_join(country_code_lookup) %>% 
  mutate(country = factor(country, levels = c("England & Wales", "Scotland", "Synthetic Germany", "Spain", "France", "Italy", "Netherlands"))) %>% 
  filter(!is.na(country)) %>% 
  filter(between(year, 1980, 2020)) %>% 
  filter(x == 65) %>% 
  ggplot(aes(x = year, y = ex, group = sex, colour = sex, linetype = sex)) + 
  geom_line() +
  facet_wrap(~country) +
  labs(
    x = "Year",
    y = "Life Expectancy at age 65",
    title = "Life expectancies at age 65 years  for selected nations",
    subtitle = "1980 to 2020 or latest available year",
    caption = "Source: Human Mortality Database"
  )
```
Equivalently:

>>>>

```{r}
hmd_ex_selected_countries_with_synth %>% 
  left_join(country_code_lookup) %>% 
  mutate(country = factor(country, levels = c("England & Wales", "Scotland", "Synthetic Germany", "Spain", "France", "Italy", "Netherlands"))) %>% 
  filter(!is.na(country)) %>% 
  filter(between(year, 1980, 2020)) %>% 
  filter(x == 0) %>% 
  ggplot(aes(x = year, y = ex, group = sex, colour = sex, linetype = sex)) + 
  geom_line() +
  facet_wrap(~country) +
  labs(
    x = "Year",
    y = "Life Expectancy at birth",
    title = "Life expectancies at birth for selected nations",
    subtitle = "1980 to 2020 or latest available year",
    caption = "Source: Human Mortality Database"
  )
```

Equivalently

@@

```{r}
hmd_ex_selected_countries_with_synth %>% 
  left_join(country_code_lookup) %>% 
  mutate(country = factor(country, levels = c("England & Wales", "Scotland", "Synthetic Germany", "Spain", "France", "Italy", "Netherlands"))) %>% 
  filter(!is.na(country)) %>% 
  filter(between(year, 1980, 2020)) %>% 
  filter(x == 65) %>% 
  ggplot(aes(x = year, y = ex, group = sex, colour = sex, linetype = sex)) + 
  geom_line() +
  facet_wrap(~country) +
  labs(
    x = "Year",
    y = "Life Expectancy at age 65",
    title = "Life expectancies at age 65 years  for selected nations",
    subtitle = "1980 to 2020 or latest available year",
    caption = "Source: Human Mortality Database"
  )
```

Equivalently:
